Intent Clarification using Fisher Information Metric

### 2018-01-02 TexFile/GopinathArgallRSS2018/GopinathArgallRSS2018.tex
First Commit

\documentclass[conference]{IEEEtran}
\usepackage{times}
% numbers option provides compact numerical references in the text. 
\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{graphicx}
\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}
\usepackage{amsmath,amssymb,latexsym,float,epsfig,subfigure}
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{lipsum}
\usepackage[export]{adjustbox}
\usepackage[normalem]{ulem} % underline
\usepackage{wrapfig}
\usepackage{multirow}
\usepackage{balance}
\usepackage{color}
\usepackage{url}
\usepackage{booktabs}
\usepackage{pifont}
\newcommand{\argmax}{\arg\!\max}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\pdfinfo{
	/Author (Deepak Gopinath, Brenna D. Argall)
	/Title  (Mode Switch Assistance to Human Intent Disambiguation)
	/CreationDate (January 31 2017)
	/Subject (Robots)
	/Keywords (Robots)
}
% numbers option provides compact numerical references in the text.

\pdfinfo{
   /Author (Homer Simpson)
   /Title  (Robots: Our new overlords)
   /CreationDate (D:20101201120000)
   /Subject (Robots)
   /Keywords (Robots;Overlords)
}

@@

% paper title
\title{Fisher Information based Disambiguation of Human Intent - An Experimental Evaluation}
\author{Author Names Omitted for Anonymous Review. Paper-ID [\textbf{163}]}
% You will get a Paper-ID when submitting a pdf file to the conference system
%\author{Deepak Gopinath and Brenna D. Argall}

%\author{\authorblockN{Deepak Gopinath}
%\authorblockA{Department of Mechanical\\Engineering,
%Northwestern University\\
%Evanston, Illinois 30332\\
%Email: deepakedakkattilgopinath2015\\@u.northwestern.edu}
%\and
%\authorblockN{Brenna D. Argall}
%\authorblockA{Department of Mechanical\\Engineering,
%		Northwestern University\\
%		Evanston, Illinois 30332\\
%		Email: brenna.argall@northwestern.edu}
%	}

%\author{Deepak Gopinath$^{1}$ and Brenna D. Argall$^{2}$
%	\thanks{Manuscript received: March, 1, 2016; Revised June,
%		7, 2016; Accepted June, 29, 2016.}
%}
% avoiding spaces at the end of the author lines is not a problem with
% conference papers because we don't use \thanks or \IEEEmembership

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\authorblockN{Deepak E. Gopinath\authorrefmark{1}\authorrefmark{2},
%		Brenna D. Argall\authorrefmark{1}\authorrefmark{2}\authorrefmark{3}\authorrefmark{4}
%	}
%	\authorblockA{
%		\authorrefmark{1}Department of Mechanical Engineering, Northwestern University, Evanston, IL}
%	
%	\authorblockA{\authorrefmark{2}Rehabilitation Institute of Chicago, Chicago, IL}
%	
%	\authorblockA{\authorrefmark{3}Department of Physical Medicine and Rehabilitation, Northwestern University, Chicago, IL}
%	
%	\authorblockA{\authorrefmark{4}Department of Electrical Engineering and Computer Science, Northwestern University, Evanston, IL}
%	
%	\authorblockA{{\tt\small deepakgopinath@u.northwestern.edu}}
%	\authorblockA{{\tt\small brenna.argall@northwestern.edu}}
%}

@@

\section{Related Work}

@@

\section{Mathematical Formalism}
\subsection{Disambiguation Schemes}
\subsubsection{Fisher Information Based Metric}
\subsubsection{Entropy-based Metric}
\subsubsection{Heuristic-based Metric}

\subsection{Intent inference}
\subsubsection{Dynamic Field Theory Based}
\subsubsection{Bayesian Inference}
\subsubsection{Confidence Functions}

\subsection{Shared Control}

\section{Experimental Evaluation}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{times}

% numbers option provides compact numerical references in the text. 
\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}
%
%\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,latexsym,float,epsfig,subfigure}
\usepackage{mathtools, bbm}
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{lipsum}
\usepackage[export]{adjustbox}
\usepackage[normalem]{ulem} % underline
\usepackage{wrapfig}
\usepackage{multirow}
\usepackage{balance}
\usepackage{color}
\usepackage{url}
\usepackage{microtype}
\usepackage{algorithm, algorithmic}
\usepackage{breqn}
\usepackage[bottom]{footmisc}
\pdfinfo{
   /Author ()
   /Title  (Robots: Our new overlords)
   /CreationDate (D:20101201120000)
   /Subject (Robots)
   /Keywords (Robots;Overlords)
}

@@

% paper title
\title{Intent Clarification using Fisher Information Metric}

% You will get a Paper-ID when submitting a pdf file to the conference system
\author{Author Names Omitted for Anonymous Review. Paper-ID [add your ID here]}

%\author{\authorblockN{Michael Shell}
%\authorblockA{School of Electrical and\\Computer Engineering\\
%Georgia Institute of Technology\\
%Atlanta, Georgia 30332--0250\\
%Email: mshell@ece.gatech.edu}
%\and
%\authorblockN{Homer Simpson}
%\authorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\authorblockN{James Kirk\\ and Montgomery Scott}
%\authorblockA{Starfleet Academy\\
%San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}}

% avoiding spaces at the end of the author lines is not a problem with
% conference papers because we don't use \thanks or \IEEEmembership

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\authorblockN{Michael Shell\authorrefmark{1},
%Homer Simpson\authorrefmark{2},
%James Kirk\authorrefmark{3}, 
%Montgomery Scott\authorrefmark{3} and
%Eldon Tyrell\authorrefmark{4}}
%\authorblockA{\authorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: mshell@ece.gatech.edu}
%\authorblockA{\authorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\authorblockA{\authorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\authorblockA{\authorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

@@

\section{Section}

@@

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.
